Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Teal isn't my favourite colour

        \begin{scope}[xshift=18cm, rotate=90]
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

@@

        \begin{scope}[xshift=25cm, rotate=90]
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

>>>>

        \begin{scope}[xshift=18cm, rotate=90]
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

@@

        \begin{scope}[xshift=25cm, rotate=90]
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
